{RandomPoints} package for \emph{Macaulay2}

### 2021-07-17 FastLinAlg/Paper/RandomRationalPoints.tex
Minor changes to the paper.

\section{Introduction}
    Let $I$ be an ideal in a polynomial ring $k[x_1,\dots, x_n]$ over a finite field $k$. Let $X:=V(I)$ denote the corresponding set of rational points in affine $n$-space. Finding one such rational point or geometric point (geometric meaning a point in some finite field extension), in an algorithmically efficient manner is our primary motivation.

>>>>

\section{Introduction}
    Let $I$ be an ideal in a polynomial ring $k[x_1,\dots, x_n]$ over a finite field $k$. Let $X:=V(I)$ denote the corresponding set of rational points in affine $n$-space. Finding one such rational point or geometric point (geometric meaning a point over some finite field extension), in an algorithmically efficient manner is our primary motivation for this package. The authors of the package are Sankhaneel Bisui, Zhan Jiang, Sarasij Maitra, Th\'ai Th\`anh Nguy$\tilde{\text{\^e}}$n, Frank-Olaf Schreyer, and Karl Schwede.
